Maaslin runs

### 2019-08-07 maaslinruns.Rmd
Typo

```{r maaslin runs, results = 'hide', eval  = TRUE} 
ret <- mclapply(var.CL.comb, function(x)
    maaslinwrapper(pseq = pseq.genus.core,
                   looped = var.BP,
                   forced = x,
                   taxa = taxa(pseq.genus.core),
                   tempstr = sprintf("%%s/combinations/maaslinruns/%%s_%s", paste0(x, collapse = "_"))),
    mc.cores = length(var.CL.comb))
```

>>>>

```{r maaslin runs, results = 'hide', eval  = TRUE} 
ret <- mclapply(var.CL.comb, function(x)
    maaslinwrapper(pseq = pseq.genus.core,
                   looped = var.BP,
                   forced = x,
                   taxa = taxa(pseq.genus.core),
                   tempstr = sprintf("%%s/maaslinruns/combinations/%%s_%s", paste0(x, collapse = "_"))),
    mc.cores = length(var.CL.comb))
```
